\documentclass{article}
\renewcommand{\familydefault}{\sfdefault}
\title{Wrting Skill Revision}
\date{2021-12-04}
\author{Jeh}

\begin{document}
    \maketitle
    \pagenumbering{arabic}

    \section{Virtual Message}
    \subsection{Interview Convey}
    Friend,\\\\
    Hello, I'm going for Interview. So,
    I have to leave early in the morning.
    I know you have a plan for a trip today but
    I am sorry for that I completely forgot about
    Interview. We will plan for the trip
    the next day,\\\\
    Thank you so much for your understanding.

    \subsection{Study Methods}
    Friend,\\\\
    Hello I recently found out about two really good
    study methods that are active recall and spaced
    repetitions. Active actively stimulate memory
    during the learning process which helps to retain
    information and Spaced repetition is an evidence-based
    learning to revise things over course of time. You could
    google to learn more about them, they've been very  
    helpful for me, I suggest you to try them out.\\\\
    Jeh

    \newpage
    \section{Statement of Purpose}
    \subsection{Business Management}
    I have always been fascinated about economic developments
    that took the place in the world. The willingness to know
    about marketing, economic and management concepts made me 
    want to pursue BBA. I aim to get inside the corporate world 
    and become a great entrepreneur. I've developed a habit of 
    reading books about economics and business management and 
    they've been very helpful for me to know about various things. 

	


\end{document}
