\documentclass{article}
\renewcommand{\familydefault}{\sfdefault}
\title{Writing Skill Revision}
\date{2021-12-04}
\author{Jeh}

\begin{document}
    \maketitle
    \pagenumbering{arabic}

    \section{Virtual Message}
    \subsection{Interview Convey} Friend,\\\\
    Hello, I'm going for Interview. So,
    I have to leave early in the morning.
    I know you have a plan for a trip today but
    I am sorry for that I completely forgot about
    Interview. We will plan for the trip
    the next day,\\\\
    Thank you so much for your understanding.

    \subsection{Study Methods}
    Friend,\\\\
    Hello I recently found out about two really good
    study methods that are active recall and spaced
    repetitions. Active actively stimulate memory
    during the learning process which helps to retain
    information and Spaced repetition is an evidence-based
    learning to revise things over course of time. You could
    google to learn more about them, they've been very  helpful for me, 
    I suggest you to try them out.\\\\
    Jeh

    \newpage
    \section{Statement of Purpose}
    \subsection{Business Management}
    I have always been fascinated about economic developments
    that took the place in the world. The willingness to know
    about marketing, economic and management concepts made me 
    want to pursue BBA. I aim to get inside the corporate world 
    and become a great entrepreneur. I've developed a habit of 
    reading books about economics and business management and 
    they've been very helpful for me to know about various things.\\
    \\ My parents have been driving force and they've always 
    encouraged me to participate in different extracurricular 
    activities. Throughout the school year I've maintained a good 
    academic record. I was in top 5 percent of my class. Also during
    my school years I've realized my potential of being a true leader.
    I've organized a large number of events, fairs and various cultural
    and educational plays. I love to socialize with people and learn
    various new things from them.\\\\
    Apart from academics, I have always been very good at sports also.
    I've also represented my school at various state level and 
    national level competitions for which I received 25 medals and
    awards.\\\\
    I strongly believe that BBA program at your university will help 
    me to nurture my skills and channel them towards my ultimate goal
    of becoming successful entrepreneur. The world-class faculty,
    infrastructure and laboratory at your university will help me to
    gain new perspective by diminishing the gap between theoretical
    studies and practical experience. I'm eagerly waiting to study
    at your university and it would be my honor to be student of 
    this magnificent institution.\\\\
    Regards,\\
    John Doe


	


\end{document}
